Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 raspi_journal.tex
Encoder goodput measurements almost done
updated acronyms list

\newcommand\floor[1]{\left\lfloor#1\right\rfloor}

@@

\noindent NC: Network Coding\\
RLNC: Random Linear Network Coding\\}

>>>>

\newcommand\floor[1]{\left\lfloor#1\right\rfloor}
\newcommand\ceil[1]{\left\lceil#1\right\rceil}

@@

% Use these two commands to get used acronyms
%used=$(grep -ohR '\\ac{[^}]*' *.tex | cut -f2 -d'{' | sort | uniq)
%for ac in ${used[@]}; do echo "$(grep -R "acro{${ac}}" acronym.tex)"; done | cut -f2-4 -d'{'
% Use text editor to replace '}{' --> ': ' and '}' --> '\\'

\noindent ACK: Acknowledgment\\
AMR: Adaptive Multi-Rate\\
ARM: Advanced RISC Machine\\
BLAS: Basic Linear Algebra Subprograms\\
CPU: Central Processing Unit\\
CSMA/CA: Carrier Sense Multiple Access with Collision Avoidance\\
GB: Gigabyte\\
D2D: Device to Device\\
DAG: Direct Acyclic Graph\\
DC: Direct Current\\
DCF: Distributed Coordination Function\\
GF: Galois Field\\
GPU: Graphic Processing Unit\\
IP: Internet Protocol\\
IPTV: Internet Protocol TeleVision\\
LAN: Local Area Network\\
l.d.: linearly dependent\\
l.i.: linearly independent\\
LNC: Linear Network Coding\\
LOS: Line Of Sight\\
MAC: Medium Access Control\\
MIMO: Multiple Input Multiple Output\\
NC: Network Coding\\
NLOS: Non Line Of Sight\\
OSI: Open Systems Interconnect\\
PC: Personal Computer\\
PNC: Physical layer Network Coding\\
QoE: Quality of Experience\\
RLNC: Random Linear Network Coding\\
SRLNC: Sparse Random Linear Network Coding\\
SIMD: Single Instruction Multiple Data\\
SIMD: Single Instruction Multiple Data\\
SMP: Symmetric Multiprocessor\\
SOC: System on Chip\\
SSE: Streaming SIMD Extensions\\
TSNC: Tunable Sparse Network Coding\\
VoIP: Voice over Internet Protocol\\
WLAN: Wireless Local Area Network\\
dof: degrees of freedom\\
IP: Internet Protocol\\
OS: Operating System\\
NFS: Network File System\\
RAM: Random Access Memory\\
Raspi: Raspberry Pi\\
SSH: Secure Shell\\
USB: Universal Serial Bus\\
SCP: Secure copy\\
Telnet: Telnet}
